---
title: "Gov 50 Final Project"
author: "Tracy Das"
description: "My final project"
output:
  distill::distill_article:
    self_contained: false
editor_options: 
  markdown: 
    wrap: 72
---

```{r}
library(dplyr)
library(tidyverse)
library(ggplot2)
##Load Data
ht_data <- read.csv("Human_trafficking_data.csv") 
```

## The Global Issue of Human Trafficking

I believe that Human trafficking is a topic not discussed enough and has
sparked my interest in analyzing trafficking victim rates on a global
scale. If we opened discussions on which global regions occupy the
largest amount of human trafficking, then we can identify which
countries have the most and highlight reasons why they are exploited. I
will also be diving into whether or not the rate of victims have
increased or decreased as years go by.

I hypothesize that human trafficking is most common in Africa and the
rate of victims overtime has tremendously increased. Variables that
influence the rate of human trafficking among countries include but are
not limited to the sex of human trafficking victims, region, 
legalization of prostitution within nations, border control guidelines,
forms of exploitation (sexual violence, forced labour, etc), age, and
GDP. Our outcome variable of interest in this study will be the rates of
human trafficking among each nation.

```{r}
library(tidyverse)
library(ggplot2)

Regions <- as.factor(ht_data$Region)

ggplot(ht_data, aes(x = Regions, fill = Regions)) +
  geom_bar() + 
  labs(x = "Global Regions", y = "Number of Human Trafficking Victims", title= "Distribution of Human Trafficking by Region")
  
#scale_fill_manual(values = c(Oceania = "steelblue1", Americas = "indianred1", Africa = "turquoise2", Asia = "orange", Europe = "maroon1", ` ` = "purple"))
```

My data source comes from the United Nations Office in Drugs & Crime
(UNDOC) detected trafficking in persons data set.
(<https://dataunodc.un.org/dp-trafficking-persons> ). This bar chart
reveals the frequency of human trafficking by region. My research design
is a before-and-after project because we are utilizing data reported
between the span of multiple years. (2017-2021).

The dependent variable in this context is the number of human
trafficking victims and our independent variables measured are the
specific global regions (Americas, Asia, Africa, Europe, and Oceania),
years, and sex. These categories are found within the
human_trafficking_data.csv.  

From the barch chart above, we see that Europe holds the highest number
of human trafficking victims compared to other global regions. Oceania
holds the least amount of human trafficking victims. In my opinion, the
reason for this is due to the population in Oceania. Oceania's
populations is fairly small and does not have many countries whereas
Europe has more nations where victims are reporting their trafficking
experiences. Asia is the second most global region with the highest
reported amount of human trafficking victims. Africa is ranked third and
the Americas is ranked fourth.

## Regression & Results

```{r}
library(modelsummary)

ht_data <- ht_data |>
  mutate(Rate = if_else(txtVALUE == "<5", 1, as.numeric(txtVALUE)))

fit <- lm(Rate ~ Year + Regions + Category, data = ht_data)
summary(fit)


modelsummary::modelsummary(fit,
                           statistic = c("s.e. = {std.error}",
                                         "p = {p.value}"),
                           gof_map = c("nobs", "r.squared", "adj.r.squared"))
```

The main coefficient of interest in my regression is the number of human
trafficking victims on a global scale. The original data set included
"\<5" in the txtValue column (rate of human trafficking victims per
country) but I mutated this rate into 1 for my dependent variable to
showcase regression.

Holding all other variables including years constant, switching Africa
(our intercept) to Asia, our human trafficking victim rates would
increase by 21.787 individuals per year. Comparing human trafficking
rates of Africa to the Americas, there are 23.984 more victims per year
in the Americas. Furthermore, Europe has 27.591 more human trafficking
victims per year compared to Africa and Oceania has 8.953 less human
trafficking victims per year compared to Africa.

After the regression, the years that went by did not have a great
significance regarding human trafficking rates. However, we can see from
the regression that the regions held the greatest impact on my dependent
variable because the global regions have the highest coefficients in my
regression table.

According to my regression table, the years variable had a coefficient
of .290 and P-value of .855. I would accept the null for years since the
P-value is greater than my chosen alpha of 0.05. Therefore, years is not
statistically significant and we should not interpret it causally.
However, I would reject the null for Regions since the P-values for
Asia, the Americas, and Europe were \<0.001. These P-values are less
than my selected alpha of 0.05. For the most part, Global regions are
statistically significant and we should interpret it causally. For
Oceania, I would accept the null because the P-value is 0.343, which is
less than my selected of 0.05. This implies that it is not statistically
significant.

```{r}
ht_data <- ht_data |>
  mutate(Asia = if_else(Region == "Asia", 1, 0),
         Americas = if_else(Region == "Americas", 1, 0),
         Africa = if_else(Region == "Africa", 1, 0),
         Europe = if_else(Region == "Europe", 1, 0),
         Oceania = if_else(Region == "Oceania", 1, 0))



ht_data |> 
  ggplot(mapping = aes(x = Year, 
                     y = Rate, na.rm = TRUE)) +
geom_jitter(alpha = 0.5) +
geom_smooth() + 
  facet_wrap(~ Region) + 
labs(x = "Years",
       y = "Number of Human Trafficking Victims")
```

As displayed above, is the number of global human trafficking rates by
region as the years have gone by. In addition, by looking at the graphs
we can see some nations have a large amount of reported Human
Trafficking victims, yet globally, there are nations that have lower
rates of trafficking victims as highlighted by the blue line which is
the line of best fit. As the years progress, the line of best fit does
not drastically increase or decrease.

## Conclusion

All in all, human trafficking is unfortunately prevalent among nations
across the world. Whether it is just one victim or over a million in a
nation, individuals are being exploited either for forced labor, sexual
pleasure, or other forms of labor which can include but are not limited
to fraud, coercion, debt bondage, and more. Globally, Europe has the
most reported human trafficking rates. If given more time and money, I
would have liked to dive deeper into these categories included in other
data sets in order to see which form of exploitation is more common,
where, and if countries facing tremendous debt have an impact on the
amount of victims exported and imported from their nation. I would also
try to identify if there is a higher prevalence of human trafficking in
countries with weaker governance structures and loopholes in law
enforcement.

The limitations I faced upon this problem and data set was the
chronically under reported victims of human trafficking. The rates of
under reported human trafficking victims varies globally, in which I
have no control over. There are some people who may be more open about
their story and the region they are located is going to affect the rate
within this data set. We are not entirely sure if Europe actually holds
the most amount of victims because not all victims are able to report
their cases.

My original hypothesis also was not proven with a drastic number or
regression. As years progressed, human trafficking rates were still
prevalent but there is a steady line of best fit, indicating how rates
did not fluctuate drastically. This poses a potential threat to
inference. Time (years) is not a cause or acts upon human trafficking
rates increasing or decreasing as I anticipated. There was neither a big
increase or decrease and statistically insignificant given the P-value
of .855 when my chosen alpha was 0.05. With more time, I could have also
conducted research on human trafficking rates using a csv with data that
covered a larger time span and not just three years (2017-2021).

\
