---
title: "Gov 50 Final Project"
author: "Tracy Das"
description: "My final project"
output:
  distill::distill_article:
    self_contained: false
editor_options: 
  markdown: 
    wrap: 72
---

## Project thoughts

I am interested in exploring data related to human trafficking rates in
the United States. I want to focus on how the U.S-Mexican boarder is one
of the main transports for human trafficking compared to other boarders
and countries globally. I also want to analyze the amount of human
trafficking cases there are around the world.

```{r}
##Load Data
ht_data <- read.csv("Human_trafficking_data.csv") 
```

## Writing Proposal

Which countries are the biggest consumers of human trafficking? I
hypothesize that human trafficking is most common among nations in
numerous debts and have the potential to exploit victims with loopholes
in their governments. Variables that influence the rate of human
trafficking among countries include but are not limited to the sex of
human trafficking victims, legalization of prostitution within nations,
border control guidelines, forms of exploitation (sexual violence,
forced labour, etc), age, and GDP. Our outcome variable of interest in
this study will be the rates of human trafficking among each nation.
Potential observed patterns in my data that could help prove my thesis
could include:

-Correlation between high levels of national debt and increased
instances of human trafficking

-Identification of a higher prevalence of human trafficking in countries
with weaker governance structures and loopholes in law enforcement.

-nations facing economic crises due to debts are more likely to turn a
blind eye to human trafficking activities within their borders.

-nations where work is commonly exploited could have a pattern of human
trafficking to help boost the GDP.

Conversely, some patterns that could disprove my hypothesis in the data
could include:

-Lack of correlation between national debt levels and incidences of
human trafficking.

-Instances of significant human trafficking in countries with sound
economic conditions and strong governance systems.

-Evidence indicating that human trafficking is equally prevalent in
nations regardless of their debt status or the strength of their
governance structures.

```{r}
library(tidyverse)
library(ggplot2)

Regions <- as.factor(ht_data$Region)

ggplot(ht_data, aes(x = Regions, fill = Regions)) + geom_bar() + labs(x = "Global Regions", y = "Number of Human Trafficking Victims", title= "Distribution of Human Trafficking by Region")
  
#scale_fill_manual(values = c(Oceania = "steelblue1", Americas = "indianred1", Africa = "turquoise2", Asia = "orange", Europe = "maroon1", ` ` = "purple"))
  
```

This bar chart reveals the frequency of human trafficking by region.
Globally, Europe holds the highest number of human trafficking victims
compared to other global regions. Oceania consumes the least amount of
human trafficking victims.
